The origin of cosmic-ray electrons in cluster outskirts

### 2012-02-05 paper.tex
new figures+text update

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
  \includegraphics[width=0.49\columnwidth]{./figures/CRspec.alphaCheck.eps}
  \includegraphics[width=0.49\columnwidth]{./figures/CRspec.snapCheck.eps}
  \caption{Testing the robustness of the CR electron spectra. Left
    panel shows how different cuts in injected spectra impact the
    total volume weighted CR electron spectrum with full cooling; no
    spectral cut (red line), cut particles with $\alpha_\inj>2.2$
    (yellow line), cut particles with $\alpha_\inj>2.4$ (green line),
    cut particles with $\alpha_\inj>2.6$ (blue line). Note that in the
    main CR model we cut all particles with an $\alpha_\inj>2.4$,
    which is a factor four smaller at low energies than the spectrum
    without a cut. Right panel shows the effect of time-resolution on
    the CR electron spectra. The median CR spectrum is shown with full
    cooling that includes radiative, Coulomb, and adiabatic losses
    (dash-dotted line), the solid line represents the total volume
    weighted CR electron spectrum with full cooling. The three line
    colors corresponds to the same cluster, a large coma like merging
    cluster, but with different time resolution between snapshots in
    the relevant regime; red lines corresponds to 100 Myrs between
    snapshots, orange lines corresponds to ~(1.0-1.5) Gyrs between
    snapshots, and the blue lines corresponds to ~(1.0-1.5) Gyrs
    between snapshots. \AP{Do we want to put these figures in an
      appendix?} \label{fig:e_spec_tests}}
\end{minipage}
\end{figure*}

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{./figures/old/CRespecRadial.Radial2Rv.a24.140.v16.eps}
  \caption{Spatial dependence of the cosmic ray electron spectra at
    redshift zero. We show the total volume weighted CR electron
    distribution function; a Coma like cluster (left panel), a massive
    cooling flow cluster (middle panel), and the median of our 14
    cluster's spectra (right panel). The different line colors show
    the CR electron spectra for different radial bins. \AP{We might
      want to put this type of figure in the second
      paper!?!}\label{fig:e_spec_spatial}}
\end{figure}

>>>>

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
  \includegraphics[width=0.33\columnwidth]{./figures/CRspec.alphaCheck.eps}
  \includegraphics[width=0.33\columnwidth]{./figures/CRspec.snapCheck.eps}
  \includegraphics[width=0.33\columnwidth]{./figures/CRspec.partCheck.eps}
  \caption{Testing the robustness of the CR electron spectra. Left
    panel shows how different cuts in injected spectra impact the
    total volume weighted CR electron spectrum with full cooling; no
    spectral cut (red line), cut particles with $\alpha_\inj>2.2$
    (yellow line), cut particles with $\alpha_\inj>2.4$ (green line),
    cut particles with $\alpha_\inj>2.6$ (blue line). Note that in the
    main CR model we cut all particles with an $\alpha_\inj>2.4$,
    which is a factor four smaller at low energies than the spectrum
    without a cut. Middle panel shows the effect of time-resolution on
    the CR electron spectra. The median CR spectrum is shown with full
    cooling that includes radiative, Coulomb, and adiabatic losses
    (dash-dotted line), the solid line represents the total volume
    weighted CR electron spectrum with full cooling. The three line
    colors corresponds to the same cluster, a large coma like merging
    cluster, but with different time resolution between snapshots in
    the relevant regime; red lines corresponds to 100 Myrs between
    snapshots, orange lines corresponds to ~(1.0-1.5) Gyrs between
    snapshots, and the blue lines corresponds to ~(1.0-1.5) Gyrs
    between snapshots. Right panel show the converegence in number of
    particles used of the CR electron spectra for three representative
    clusters. We find that 1000 particles is enough to represent the
    CRs within the (1.3-1.5)$\rvir$ region of the clusters. \AP{Do we
      want to put these figures in an
      appendix?} \label{fig:e_spec_tests}}
\end{minipage}
\end{figure*}

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{./figures/CRespecRadial.g72a.2Rv15000p.a24.full.140.v21.eps}
  \caption{Spatial dependence of the cosmic ray electron spectra at
    redshift zero. We show the total volume weighted CR electron
    distribution function; a Coma like cluster (left panel), a massive
    cooling flow cluster (middle panel), and the median of our 14
    cluster's spectra (right panel). The different line colors show
    the CR electron spectra for different radial bins. \AP{Add other
      clusters. We might want to put this type of figure in the second
      paper!?!}\label{fig:e_spec_spatial}}
\end{figure}

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{./figures/FluxMach.1.4Rv.a24.full.020.v21.eps}
  \caption{Flux from radio relics and the associated Mach numbers. We
    show the observed radio relic fluxes at 1.4 GHz (diamonds) and
    their Mach numbers as derived from radio spectral index. We
    contrast the observations with the predicted fluxes (X) where the
    error bars corresponds to the 68 percentiles of the volume
    weighted CR electron spectra across our cluster sample. The dashed
    line show the expected flux of a typical relic where we only
    change the Mach number. \AP{THREE HIGH MACH NUMBER RELICS NO SPECTRAL
    INDEX, NEED TO LOOK IN LITERATURE. MIGHT WANT TO INCLUDE LOFAR
    PREDICTIONS AS WELL?}\label{fig:Fluc_Mach}}
\end{figure}
